{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-12-01 main.tex
update main.tex / added two articles to .bib

		\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the application)
		\item Present Results
		\item Explain relevance for application
	\end{itemize}

>>>>

		\item Prediction not Inference (Alternative: Focused on a testing procedure motivated by the application)
		\item Present Results
		\item Explain relevance for application
	\end{itemize}
	\subsection{Motivate Simulation for some data generating process from application}
	For the simulation study, we use Reiss and Ogden (2007) as a guideline. Similar to them, we will use the gasoline dataset in order to predict the octane rating of gasoline samples by relying on the introduced methods. This has become more relevant as modern internal combustion engines become more complex and rely on precisely tuned fuels. The dataset, which contains 60 observations with each 400 measurements was constructed using Near infra-red (NIR) spectroscopy, which allows to analyse samples of gasoline much faster and with the same reproducibility as standard tests (cf. \cite{Bohacs_Ovadi_Salgo1998}). Similar to Reiss and Ogden (2007), two different true coefficient functions $f_1$ and $f_2$ were chosen that differ in their smoothness: 
\begin{equation}
    f_1 = 2\sin(0.5\pi*t) + 4\sin(1.5\pi*t) + 5*\sin(2.5*\pi*t) 
    \end{equation}
    \begin{equation}
    f_2 = 1.5^{\frac{-0,5(t-0.3)^2}{0.02^2}} - 4^{\frac{-0,5(t-0.45)^2}{0.015^2}} +  8^{\frac{-0,5(t-0.6)^2}{0.02^2}} -  1^{\frac{-0,5(t-0.8)^2}{0.03^2}}
    \end{equation}

Two different error-terms $\epsilon $ were created by first generating iid standard normal error and then multiplying them by $\sigma_e $ which is calculated such that the squared multiple correlation coefficient $R^2 = var(X\omega) / (var(X\omega) + \sigma^2_{e})$ is equal to 0.9 and 0.6. These two error-terms are than computed to generate two sets of responses with different signal-to-noise ratios for each true function, using the gasoline dataset. These four combinations are then used with different number of basis-function $(5,6,...,25)$ of the order 5 to predict the responses using the b-spline basis approach and the FPCR approach. Within one repetition, the data is randomly sampled into a training and a test set to calculate the reported test MSE. In total we carried out 2000 simulations for each combination of data and number of basis functions.
